Verifying Spatial Properties of Array Computations

### 2017-04-14 oopsla17/oopsla17.tex
Fix style of definitions
Specify dimensionality in subscript

\theoremstyle{defn}
\newtheorem{defn}{Definition}

@@

\begin{defn}[Array subscripts and indices]
  An \emph{array subscript}, denoted $a(\bar{e})$, is an expression
  which reads from an array $a$ at an \emph{index} specified by a
  comma-separated sequence of integer expressions denoted $\bar{e}$ or
  in expanded form as $(e_1, \ldots, e_n)$. An index $e_i$ is called
  \emph{relative} if the expression involves an induction variable.
  An \emph{absolute index} is a integer expression which is constant
  relative to the enclosing loop.
\end{defn}

>>>>

\theoremstyle{definition}
\newtheorem{defn}{Definition}

@@

\begin{defn}[Array subscripts and indices]
  An \emph{array subscript}, denoted $a(\bar{e})$, is an expression which reads
  from an $N$-dimensional array $a$ at an \emph{index} specified by a
  comma-separated sequence of integer expressions denoted $\bar{e}$ or in
  expanded form as $(e_1, \ldots, e_N)$. An index $e_i$ is called
  \emph{relative} if the expression involves an induction variable. An
  \emph{absolute index} is a integer expression which is constant relative to
  the enclosing loop.
\end{defn}
